Stack Safety as a Security Property

### 2020-07-01 main.tex
More polishing on the contributions (but they need even more!)

In summary, we offer the following contributions:
\begin{itemize}
\item \leo{More? Extensional} formal characterizations of the
  intuitive concepts of local state encapsulation~\ref{sec:lse} and
  well-bracketed control flow~\ref{sec:wbcf}.  Evidence that this
  property is strong enough to capture the folk intuition: we show
  that the stack unsafe examples from the literature also fail our
  property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed micropolicy enforcement
  mechanism~\ref{sec:micropolicy}. \leo{And it says yes on a
    substantial body of code} We then present a variation of the
  property + policy that is lazy, easier/more efficient to implement,
  and provably weaker.
\item A provably stronger (inductive? step-by-step/stepwise) variant
  of this property tuned for testing/verification.  We test the whole
  thing with a cool framework.
\end{itemize}
We begin with some technical preliminaries in
Section~\ref{sec:prelim}. Section~\ref{sec:relwork} discusses related work, and
Section~\ref{sec:future} sketches directions for future work.

@@

\section{Stack Safety, Formally}

@@

\section{Discussion}

@@

\section{Lazy Stack Safety}

>>>>

In summary, we offer the following contributions:
\begin{itemize}
\item \leo{More? Extensional}\bcp{We might need to invent a word for this---''quasi-extensional''?} formal characterizations of the
  intuitive concepts of local state encapsulation and
  well-bracketed control flow~(\Cref{sec:lse-and-wbcf}).  As evidence that this
  property is strong enough to capture the folk intuition, we show
  that the stack unsafe examples from the literature also fail our
  property~(\Cref{sec:disc}).
\item As evidence that the property is not too strong, we show that it is
  realizible by
  a previously proposed micropolicy enforcement
  mechanism~(\Cref{sec:micropolicy}). \leo{And it says yes on a
    substantial body of code}. We also present a variation of the
  property + policy that is lazy, easier/more efficient to implement,
  and provably weaker (\Cref{sec:lazy}).
\item A provably stronger (inductive? step-by-step/stepwise) variant
  of this property tuned for testing/verification.  We test the whole
  thing with a cool framework. \bcp{Which section?}
\end{itemize}
Section~\ref{sec:relwork} discusses related work, and
Section~\ref{sec:future} sketches directions for future work.
%
We begin with some technical preliminaries in
Section~\ref{sec:prelim}.

@@

\section{Stack Safety, Formally}
\label{sec:lse-and-wbcf}

@@

\section{Discussion}
\bcp{Make this a subsection?}
\label{sec:disc}

@@

\section{Lazy Stack Safety}
\label{sec:lazy}
